Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-05 article.tex
MHC-I epitopes that are not immunogenic are non-existing or rare

Transmembrane helices (TMHs) in the human proteome
are an overrepresented potential source of epitopes on major 
histocompatibility complex (MHC) class I for the majority of HLA-I haplotypes. 
It is unknown if the immune system is as able to detect those 
TMHs present in pathogens.
Additionally, it is unknown if TMH-II is also likelier to detect
human and pathogen TMHs than expected by chance.
It is unknown if natural selection is the cause that 
the immune system is more attentive for TMHs
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to polypeptides derived from TMHs 
[less/equally/more] often than expected by chance.
Lastly, we show that natural selection on TMHs is [strong enough/still too weak]
to detect.
Our findings suggest that the immune system is [less/neutral/more]
vigilant to TMHs than expected by chance and this has 
left [a clear/a weak/no]
signal in the evolutionary history of the pathogen.

@@

@@

We assume that if a polypeptide binds to an MHC, it is always presented and always
leads to an immune response. We know this is not the case \richel{for example,
I know this from Frans :-)}, but we do not know how common this is 
\richel{read literature to find out}. The more often this phenomenon occurs,
the more our analysis is weakened.

>>>>

Transmembrane helices (TMHs) in the human proteome
are an overrepresented potential source of epitopes on major 
histocompatibility complex (MHC) class I for the majority of HLA-I haplotypes. 
It is unknown if the immune system is as able to detect those 
TMHs present in pathogens.
Additionally, it is unknown if TMH-II is also likelier to detect
human and pathogen TMHs than expected by chance.
It is unknown if natural selection is the cause that 
the immune system is more attentive for TMHs
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to polypeptides derived from TMHs 
[less/equally/more] often than expected by chance.
Lastly, using an unprecedented sharp method, 
we show that natural selection on TMHs is [strong enough/still too weak]
to detect.
Our findings suggest that the immune system is [less/neutral/more]
vigilant to TMHs than expected by chance and this has 
left [a clear/a weak/no]
signal in the evolutionary history of the pathogen.

@@

We can predict epitopes.
For MHC-I, \verb;epitope-prediction; is used \richel{Cite Johannes}.
For MHC-II, NetMHCIIpan uses all haplotypes \richel{Cite Morten}.
Although \cite{zhang2015accurate} looks like an even better
method for MHC-II, they only take one haplotype into account.

@@

We assume that if a polypeptide binds to an MHC, it is always presented and always
leads to an immune response.
The more often this assumption is violated, 
the more our analysis will be weakened.
Experiments in mice with MHC-I epitopes, however, indicate that (if the dose 
administered was high enough) there are either none or rare
exceptions \cite{sette1994relationship}.
